---
title: "21.05.20_RPCAD check"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr)
library(cowplot)
```

## This seems to have been done in May of 2020
## CAD cells, all 3'TOPs (with some RPL7 5'TOPs?)

```{r, mature RNA summary}

CAD_summary <- as_tibble(read.csv("21.05.20_RPCADFISH/Results/__FQ_batch_summary_MATURE_210524.txt", skip = 4, header = TRUE, sep = "\t"))

CAD <-  CAD_summary %>% 
  separate(FILE, sep = "_", into = c("CAD", "gene", "image", "extra", "STACK", "extra2")) %>% 
  mutate(cell = as.numeric(substr(CELL, 6, 6)), 
         cell = ifelse(cell %% 2 == 0, "neurite", "soma"),
         image = substr(image,1,2)) %>% 
  dplyr::select(gene, image, cell, AREA_cell, N_total, N_thres_Total)

```

```{r, all spot tidy data}
all_spot_cad <- as_tibble(read.csv("21.05.20_RPCADFISH/Results/_FISH-QUANT__all_spots_210525.txt", header = TRUE, skip = 13, sep = "\t"))

all_spot_cad <- all_spot_cad %>% separate(File, into = c("CAD", "gene","image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), cell = ifelse(cell %% 2 == 0, "neurite", "soma"), image = substr(image,1,2)) %>% select(gene, image, cell, everything(), -stack) 

```

```{r, all spot filter}
all_spot_cad %>% select(gene,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + facet_wrap(cell~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
all_spot_cad  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>%  select(group,cell, AMP, INT_raw, INT_filt) %>% gather(-group,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(cell~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
all_spot_cad %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,cell,INT_raw) %>% gather(-group,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(1000,3500) + facet_grid(.~cell) + geom_hline(yintercept = 2250)

all_spot_cad %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,cell,BGD) %>% gather(-group,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(400,1100) + facet_grid(.~cell) + geom_hline(yintercept = 775)

all_spot_cad %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,cell,Pos_Z) %>% gather(-group,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + theme_cowplot()  + facet_grid(.~cell) + geom_hline(yintercept = 450) + geom_hline(yintercept = 7000) + ylim(-500,7500)

all_spot_cad %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,cell,SigmaX) %>% gather(-group,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + theme_cowplot()  + facet_grid(.~cell) + geom_hline(yintercept = 200)

all_spot_cad %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,cell,SigmaZ) %>% gather(-group,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + theme_cowplot() + facet_grid(.~cell) + geom_hline(yintercept = 500)


#really limits spots.
CAD_filt <- all_spot_cad %>% filter(as.numeric(SigmaX) < 200, as.numeric(SigmaZ) < 500, as.numeric(INT_raw) < 8000, as.numeric(INT_raw) > 2500, TH_fit == 1) #, as.numeric(BGD) > 775, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
CAD_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,image,cell,Cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = cell)) + geom_boxplot() + theme_cowplot()

CAD_filt %>% filter(gene != "5TOP28", gene != "5TOP7", gene != "5TOP7mut") %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,image,cell,Cell) %>% summarize(numspots = n()) %>% filter(cell == "soma") %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + stat_compare_means(comparisons = list(c("pTL005", "3TOP7"), c("pTL005", "3TOP7mut"), c("pTL005", "3TOP28"), c("pTL005", "3TOP28mut"),c("3TOP28", "3TOP28mut"),c("3TOP7", "3TOP7mut")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite") + guides(fill = FALSE) + EnvStats::stat_n_text(y.pos = -10)

CADfilt_summary <- CAD_filt %>% group_by(gene,image,cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene, image, cell, N_thres_Total) %>% 
  group_by(gene,image) %>% 
  spread(key = cell, value = N_thres_Total) %>%
  mutate(n_s_thresh = neurite/soma) %>% 
  select(gene, image, n_s_thresh) %>% 
  ungroup() %>% left_join(., CAD_filt %>% group_by(gene,image,cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene, image, cell, N_thres_Total)) 

CADfilt_summary %>% select(-N_thres_Total) %>% filter(gene != "5TOP28", gene != "5TOP7", gene != "5TOP7mut", gene != "Lox") %>% unique() %>% ggplot(aes(x = gene, y = n_s_thresh))  + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA, width = 0.1) + theme_cowplot() + stat_compare_means(comparisons = list(c("pTL005", "3TOP7"), c("pTL005", "3TOP7mut"), c("pTL005", "3TOP28"), c("pTL005", "3TOP28mut"),c("3TOP28", "3TOP28mut"),c("3TOP7", "3TOP7mut")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = FALSE, alpha = FALSE) + scale_x_discrete(limits = c("pTL005", "3TOP7", "3TOP7mut", "3TOP28", "3TOP28mut"), labels = c("Firefly", "RPL7\n3'TOP", "RPL7mut\n3'TOP", "RPS28\n3'TOP", "RPS28mut\n3'TOP"))  + scale_fill_manual(values = c("#b82080", "#b82080","#e8c040", "#e8c040", "#808080")) + scale_alpha_manual(values = c(1,0.5,1,0.5,1)) + EnvStats::stat_n_text(y.pos = -0.01)


```

```{r, }
n_s_tot <- CAD %>% filter(gene !="Lox") %>%
  select(gene, image, cell, N_total) %>% 
  group_by(image) %>% 
  mutate(id=rep(1:(n()/2),each = 2)) %>% 
  spread(key = cell, value = N_total) %>% 
  mutate(n_s_tot = neurite/soma) %>%
  select(gene, image, n_s_tot) %>% 
  ungroup() %>% 
  mutate(id = c(1:nrow(.)))

n_s_thresh <- CAD %>% filter(gene !="Lox") %>%
  select(gene, image, cell, N_thres_Total) %>% 
  group_by(image) %>% 
  mutate(id=rep(1:(n()/2),each=2)) %>% 
  spread(key = cell, value = N_thres_Total) %>%
  mutate(n_s_thresh = neurite/soma) %>% 
  select(gene, image, n_s_thresh) %>% 
  ungroup() %>% 
  mutate(id = c(1:nrow(.)))

#join these data sets and merge back with un-normalized data

rel_dat <- left_join(n_s_tot, n_s_thresh)
```

```{r,  }

CAD %>% ggplot(aes(x = gene, y = N_thres_Total, fill = cell))  + geom_boxplot(width = 0.25, outlier.shape = NA) + geom_point(alpha = 0.1, position = position_jitterdodge()) + theme_cowplot()  + labs(x = "", y = "Total Number of Spots")

CAD %>% ggplot(aes(x = gene, y = AREA_cell, fill = cell)) + geom_boxplot(width = 0.25) + geom_point(alpha = 0.1, position = position_jitterdodge()) + theme_cowplot() + labs(x = "", y = "Area")

```

```{r, }
my_comparisons = list(c("3TOP28", "3TOP28mut"), c("3TOP7", "3TOP7mut"),c("5TOP7", "5TOP7mut"), c("pTL005", "3TOP28"), c("pTL005", "3TOP28mut"), c("pTL005", "3TOP7"), c("pTL005", "3TOP7mut"), c("pTL005", "5TOP7"), c("pTL005", "5TOP7mut"), c("pTL005", "5TOP28"))

CAD %>% filter(gene != "Lox", cell == "soma") %>% ggplot(aes(x = gene, y = N_thres_Total)) + geom_point(alpha = 0.1, position = "jitter") + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), width = 0.25) + stat_compare_means(comparisons = my_comparisons, method = "wilcox.test") + theme_cowplot() + guides(fill = FALSE, alpha = FALSE) + labs(x = "", y = "Reporter Transcripts\nin Neurite") + EnvStats::stat_n_text() #+ scale_x_discrete(limits = c("pTL005", "WT3TOP", "mut3TOP"), labels = c("Firefly", "WT 3'TOP", "mut 3'TOP")) + scale_fill_manual(values = c("#00a0b0", "#808080", "#00a0b0")) + scale_alpha_manual(values = c(0.3,1,1))



rel_dat %>% ggplot(aes(x = gene, y = n_s_thresh)) + geom_point(alpha = 0.1, position = "jitter") + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), width = 0.25) + stat_compare_means(comparisons = my_comparisons, method = "wilcox.test", label.y = c(0.25,0.3,0.35)) + theme_cowplot() + guides(fill = FALSE, alpha = FALSE) + labs(x = "", y = "Reporter Transcripts\nin Neurite / Soma") + EnvStats::stat_n_text() #+ scale_x_discrete(limits = c("pTL005", "WT3TOP", "mut3TOP"), labels = c("Firefly", "WT 3'TOP", "mut 3'TOP")) + scale_fill_manual(values = c("#00a0b0", "#808080", "#00a0b0")) + scale_alpha_manual(values = c(0.3,1,1))


```


## Redo with 3'TOPs fresh thaw 9/2/21
## CAD cells with for some reason no RPS28 WT 3'TOP?

```{r, }
sept2_cad <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.09.02_CAD3TOP/Results/_FISH-QUANT__all_spots_210909.txt", header = TRUE, skip = 13, sep = "\t"))

sept2_cad <- sept2_cad %>% separate(File, into = c("CAD", "gene", "3TOP", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), cell = ifelse(cell %% 2 == 0, "neurite", "soma"), image = substr(image,1,2)) %>% select(gene, image, cell, everything(), -stack, -`3TOP`) 

```

```{r, }
sept2_cad %>% select(gene,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + facet_wrap(cell~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
sept2_cad  %>% select(gene,cell, AMP, INT_raw, INT_filt) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + facet_wrap(cell~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
sept2_cad %>%  select(gene,cell,INT_raw) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(1000,3500) + facet_grid(.~cell) + geom_hline(yintercept = 1750)

sept2_cad %>% select(gene,cell,BGD) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(200,1100) + facet_grid(.~cell) + geom_hline(yintercept = 775)

sept2_cad %>% select(gene,cell,Pos_Z) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + facet_grid(.~cell) + geom_hline(yintercept = 450) + geom_hline(yintercept = 7000) + ylim(-500,7500)



#really limits spots.
sept2_cad_filt <- sept2_cad %>% filter(TH_fit == 1, as.numeric(INT_raw) < 5000, as.numeric(INT_raw) > 1750) %>% filter(!(gene == "FF" & image %in% c("01", "03")), !(gene == "RPS28mut" & image %in% c("01", "07","08"))) #, as.numeric(BGD) > 775, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
sept2_cad_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,image,cell,Cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = cell)) + geom_boxplot() + theme_cowplot() 

sept2_cad_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,image,cell,Cell) %>% summarize(numspots = n()) %>% filter(cell == "soma") %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28mut"), c("RPL7", "RPL7mut")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite") + guides(fill = "none") + EnvStats::stat_n_text(y.pos = -10) + ggtitle("3'TOP CONSTRUCTS")

sept2_cad_filt_summary <- sept2_cad_filt %>% group_by(gene,image,cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene, image, cell, N_thres_Total) %>% 
  group_by(gene,image) %>% 
  spread(key = cell, value = N_thres_Total) %>%
  mutate(n_s_thresh = neurite/soma) %>% 
  select(gene, image, n_s_thresh) %>% 
  ungroup() %>% left_join(., sept2_cad_filt %>% group_by(gene,image,cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene, image, cell, N_thres_Total)) 

sept2_cad_filt_summary %>% select(-N_thres_Total) %>% filter(cell == "soma") %>% ggplot(aes(x = gene, y = n_s_thresh))  + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA, width = 0.1) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28mut"), c("RPL7", "RPL7mut")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = "none", alpha = "none") + scale_x_discrete(limits = c("FF", "RPL7", "RPL7mut", "RPS28mut"), labels = c("Firefly", "RPL7\n3'TOP", "RPL7mut\n3'TOP", "RPS28mut\n3'TOP")) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,0.5)) + EnvStats::stat_n_text(y.pos = -0.01)
```


## more Redo with 3'TOPs fresh thaw 9/18/21 cuz RPS28 looked like crap
## This is why. more FISH with just RPS28 WT and mut 3'TOPs

```{r, }
sept18_cad <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.09.15_CAD3TOP/Results/_FISH-QUANT__all_spots_210919.txt", header = TRUE, skip = 13, sep = "\t"))

sept18_cad <- sept18_cad %>% separate(File, into = c("CAD", "3TOP", "gene", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), cell = ifelse(cell %% 2 == 0, "neurite", "soma"), image = substr(image,1,2)) %>% select(gene, image, cell, everything(), -stack, -`3TOP`) 

```

```{r, }
sept18_cad %>% select(gene,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + facet_wrap(cell~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
sept18_cad  %>% select(gene,cell, AMP, INT_raw, INT_filt) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + facet_wrap(cell~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
sept18_cad %>%  select(gene,cell,INT_raw) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(400,3500) + facet_grid(.~cell) + geom_hline(yintercept = 1250)

sept18_cad %>% select(gene,cell,BGD) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(200,1100) + facet_grid(.~cell) + geom_hline(yintercept = 775)

sept18_cad %>% select(gene,cell,Pos_Z) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + facet_grid(.~cell) + geom_hline(yintercept = 450) + geom_hline(yintercept = 7000) + ylim(-500,7500)



#really limits spots.
sept18_cad_filt <- sept18_cad %>% filter(TH_fit == 1, as.numeric(INT_raw) < 5000, as.numeric(INT_raw) > 1250) %>% filter(!(gene == "RPS28" & image %in% c("01", "03")), gene != "FF") #, as.numeric(BGD) > 775, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
sept18_cad_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,image,cell,Cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = cell)) + geom_boxplot() + theme_cowplot() 

sept18_cad_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,image,cell,Cell) %>% summarize(numspots = n()) %>% filter(cell == "soma") %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28mut"), c("RPL7", "RPL7mut")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite") + guides(fill = "none") + EnvStats::stat_n_text(y.pos = -10) + ggtitle("3'TOP CONSTRUCTS")

sept18_cad_filt_summary <- sept18_cad_filt %>% group_by(gene,image,cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene, image, cell, N_thres_Total) %>% 
  group_by(gene,image) %>% 
  spread(key = cell, value = N_thres_Total) %>%
  mutate(n_s_thresh = neurite/soma) %>% 
  select(gene, image, n_s_thresh) %>% 
  ungroup() %>% left_join(., sept18_cad_filt %>% group_by(gene,image,cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene, image, cell, N_thres_Total)) 

sept18_cad_filt_summary %>% select(-N_thres_Total) %>% unique() %>% ggplot(aes(x = gene, y = n_s_thresh))  + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA, width = 0.1) + theme_cowplot() + stat_compare_means(comparisons = list( c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = "none", alpha = "none") + scale_x_discrete(limits = c("RPS28", "RPS28mut"), labels = c("RPS28\n3'TOP", "RPS28mut\n3'TOP")) + scale_fill_manual(values = c( "#b82080","#b82080")) + scale_alpha_manual(values = c(1,0.5)) + EnvStats::stat_n_text(y.pos = -0.01)

```

## Add it together!
## (just the most recent Thawed stuff)
```{r, }
rbind(sept2_cad_filt_summary, sept18_cad_filt_summary) %>% select(-N_thres_Total) %>% filter(cell == "soma") %>% ggplot(aes(x = gene, y = n_s_thresh))  + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA, width = 0.1) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"), c("RPL7", "RPL7mut"),c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(0.2,0.25,0.275,0.3,0.225,0.25)) + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = "none", alpha = "none") + scale_x_discrete(limits = c("FF", "RPL7", "RPL7mut","RPS28", "RPS28mut"), labels = c("Firefly", "RPL7\n3'TOP", "RPL7mut\n3'TOP", "RPS28\n3'TOP", "RPS28mut\n3'TOP")) + scale_fill_manual(values = c("#808080","#D0512E", "#D0512E", "#6e508d","#6e508d")) + scale_alpha_manual(values = c(1,1,0.65,1,0.65)) + EnvStats::stat_n_text(y.pos = -0.01)

```


## OK another round with another thaw to get more samples

```{r, }
oct22_cad <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.10.25_CAD3TOP/Results/_FISH-QUANT__all_spots_211025.txt", header = TRUE, skip = 13, sep = "\t"))

oct22_cad <- oct22_cad %>% mutate(File = ifelse(startsWith(File,"C3-"), substr(File,4,nchar(File)), File)) %>% separate(File, into = c("CAD", "gene", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), cell = ifelse(cell %% 2 == 0, "neurite", "soma"), image = substr(image,1,2)) %>% select(gene, image, cell, everything(), -stack, -CAD) 

```

```{r, }

##a closer look with each condition.
oct22_cad %>%  select(gene,cell,INT_raw) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(1000,3500) + facet_grid(.~cell) + geom_hline(yintercept = 1750)

oct22_cad %>% select(gene,cell,BGD) %>% gather(-gene,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(200,1100) + facet_grid(.~cell) + geom_hline(yintercept = 775)

#really limits spots.
oct22_cad_filt <- oct22_cad %>% filter(TH_fit == 1, as.numeric(INT_raw) < 5000, as.numeric(INT_raw) > 1750) 
```

```{r, }
oct22_cad_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,image,cell,Cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = cell)) + geom_boxplot() + theme_cowplot() 

oct22_cad_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,image,cell,Cell) %>% summarize(numspots = n()) %>% filter(cell == "soma") %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28mut"), c("RPL7", "RPL7mut")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite") + guides(fill = "none") + EnvStats::stat_n_text(y.pos = -10) + ggtitle("3'TOP CONSTRUCTS")

oct22_cad_filt_summary <- oct22_cad_filt %>% group_by(gene,image,cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene, image, cell, N_thres_Total) %>% 
  group_by(gene,image) %>% 
  spread(key = cell, value = N_thres_Total) %>%
  mutate(n_s_thresh = neurite/soma) %>% 
  select(gene, image, n_s_thresh) %>% 
  ungroup() %>% left_join(., oct22_cad_filt %>% group_by(gene,image,cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene, image, cell, N_thres_Total)) 

oct22_cad_filt_summary %>% select(-N_thres_Total) %>% filter(cell == "soma") %>% ggplot(aes(x = gene, y = n_s_thresh))  + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA, width = 0.1) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28"),c("FF", "RPS28mut"), c("RPL7", "RPL7mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = "none", alpha = "none") + scale_x_discrete(limits = c("FF", "RPL7", "RPL7mut", "RPS28","RPS28mut"), labels = c("Firefly", "RPL7\n3'TOP", "RPL7mut\n3'TOP", "RPS28\n3'TOP", "RPS28mut\n3'TOP")) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + EnvStats::stat_n_text(y.pos = -0.01)
```

## now add it ALL together

```{r, }
rbind(sept2_cad_filt_summary, sept18_cad_filt_summary) %>% rbind(., oct22_cad_filt_summary) %>% select(-N_thres_Total) %>% filter(cell == "soma") %>% filter(n_s_thresh < 0.4) %>% ggplot(aes(x = gene, y = n_s_thresh))  + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA, width = 0.1) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"), c("RPL7", "RPL7mut"),c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(0.2,0.25,0.275,0.3,0.225,0.25)) + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = "none", alpha = "none") + scale_x_discrete(limits = c("FF", "RPL7", "RPL7mut","RPS28", "RPS28mut"), labels = c("Firefly", "RPL7\n3'TOP", "RPL7mut\n3'TOP", "RPS28\n3'TOP", "RPS28mut\n3'TOP")) + scale_fill_manual(values = c("#808080","#D0512E", "#D0512E", "#6e508d","#6e508d")) + scale_alpha_manual(values = c(1,1,0.65,1,0.65)) + EnvStats::stat_n_text(y.pos = -0.01)

nsThresh_5TOP <- tibble(`5'TOP` = c("28", "28mut", "7", "7mut"), #"005",
                        med_ns = c(0.203, 0.0420, 0.196, 0.0455)) #0.0237, 

# the old FF is a little more loc than this FF... subtract difference?
# 0.0237 vs 0.0127
# diff = 0.011
nsThresh_5TOP_norm <- nsThresh_5TOP %>% mutate(norm_ns = med_ns-0.011)

rbind(sept2_cad_filt_summary, sept18_cad_filt_summary) %>% rbind(., oct22_cad_filt_summary) %>% select(-N_thres_Total) %>% filter(cell == "soma") %>% filter(n_s_thresh < 0.4) %>% ggplot(aes(x = gene, y = n_s_thresh)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"), c("RPL7", "RPL7mut"),c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(0.2,0.25,0.275,0.3,0.225,0.25)) + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = "none", alpha = "none") + scale_x_discrete(limits = c("FF", "RPL7", "RPL7mut","RPS28", "RPS28mut"), labels = c("Firefly", "RPL7\n3'TOP", "RPL7mut\n3'TOP", "RPS28\n3'TOP", "RPS28mut\n3'TOP")) + scale_fill_manual(values = c("#808080","#D0512E", "#D0512E", "#6e508d","#6e508d")) + EnvStats::stat_n_text(y.pos = -0.01) + geom_hline(data = nsThresh_5TOP, aes(yintercept = med_ns, col = `5'TOP`, alpha = `5'TOP`), size = 0.5, linetype = "dashed") + scale_color_manual(values = c("#b82080", "#b82080", "#e8c040", "#e8c040")) + scale_alpha_manual(values = c(1,0.5,1,0.5,1,1,0.6,1,0.6))

```

```{r, }
TOP5 <- as_tibble(read.table("CAD_RP_n_s_plot_data.txt"))

TOP5 <- TOP5 %>% mutate(TOP = "5'TOP", gene = ifelse(gene == "005", "FF", ifelse(gene == "28", "RPS28", ifelse(gene == "7", "RPL7", ifelse(gene == "28mut", "RPS28mut", ifelse(gene == "7mut", "RPL7mut", "na"))))))

TOP3 <- rbind(sept2_cad_filt_summary, sept18_cad_filt_summary) %>% rbind(., oct22_cad_filt_summary) %>% select(-N_thres_Total) %>% filter(cell == "soma") %>% filter(n_s_thresh < 0.4) %>% mutate(TOP = "3'TOP") %>% select(-cell)

rbind(TOP5,TOP3) %>% filter(gene %in% c("RPL7", "RPS28")) %>% mutate(sample = paste(TOP,gene,sep = "_")) %>% ggplot(aes(x = TOP, y = n_s_thresh)) + geom_boxplot(aes(fill = sample),position = "dodge", outlier.shape = NA) + stat_compare_means(comparisons = list(c("5'TOP", "3'TOP")), method = "wilcox.test", label.y = 0.5, label = "p.signif", size = 7, hide.ns = TRUE, vjust = 0.5) + facet_grid(.~gene) + scale_x_discrete(limits = c("5'TOP", "3'TOP"), labels = c("5'","3'")) + theme_cowplot() + guides(fill = FALSE) + scale_fill_manual(values = c("#D0512E", "#6e508d", "#e8c040", "#b82080")) + coord_cartesian(ylim = c(-0.01,0.6)) + labs(y = "Reporter Transcripts\nin Neurite/Soma") + theme(strip.background = element_rect(color = "white", fill = "white")) + theme(text = element_text(size=18), axis.text = element_text(size = 16)) + EnvStats::stat_n_text(y.pos = -0.01, size = 5)


```

## Larp1 siRNAs on 3'TOP expressing cells
### all cells were dox induced and siRNA transfected on day -4 for 48hr. Cells were plated on glass and media was swapped for -FBS (day -2). cells were prepped for imaging 2 days later (day 0).


```{r, 3TopLarpKD data}
Larp3top <- rbind(as_tibble(read.csv("21.11.02_CAD3TOPLarp1/Results/_FISH-QUANT__all_spots_211103.txt", header = TRUE, skip = 13, sep = "\t")), as_tibble(read.csv("21.11.02_CAD3TOPLarp1/Results/_FISH-QUANT__all_spots2_211103.txt", header = TRUE, skip = 13, sep = "\t")))


Larp3top <- Larp3top %>% separate(File, into = c("CAD", "gene", "3TOP", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), cell = ifelse(cell %% 2 == 0, "neurite", "soma"), image = substr(image,1,2)) %>% select(gene,siRNA, image, cell, everything(), -stack, -`3TOP`) %>% rowwise() 

```

```{r, 3TopLarpKD filter}

Larp3top %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(200,1000) + facet_grid(.~cell) + geom_hline(yintercept = 750)

Larp3top %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(100,600) + facet_grid(.~cell) + geom_hline(yintercept = 775)

Larp3top %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + facet_grid(.~cell) + geom_hline(yintercept = 200)

Larp3top %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + facet_grid(.~cell) + geom_hline(yintercept = 500)


#really limits spots.
Larp3top_filt <- Larp3top %>% filter(as.numeric(INT_filt) > 750, as.numeric(INT_raw) < 3000 ) #, as.numeric(BGD) > 750, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)

```


```{r, 3TopLarpKD plot}
Larp3top_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,siRNA,image,cell,Cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene, alpha = gene)) + geom_boxplot() + theme_cowplot() + facet_wrap(siRNA~cell, nrow = 3) + scale_fill_manual(values = c("#808080","#D0512E", "#D0512E", "#6e508d","#6e508d")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))

Larp3top_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,siRNA,image,cell,Cell) %>% summarize(numspots = n()) %>% spread(cell,numspots) %>% mutate(totspots = neurite + soma) %>% ggplot(aes(x = siRNA, y = totspots, fill = siRNA)) + geom_boxplot() + theme_cowplot() + facet_wrap(.~gene, nrow = 3) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "Larp1")), method = "wilcox.test") + ylab("Total Spots") + guides(fill = FALSE)  + EnvStats::stat_n_text(y.pos = -50) + scale_x_discrete(limits = c("NC1",  "Larp1"))

Larp3top_filt %>% mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>%  group_by(gene,siRNA,image,cell,Cell) %>% summarize(numspots = n()) %>% filter(cell == "soma")  %>% ggplot(aes(x = siRNA, y = numspots, fill = siRNA)) + geom_boxplot() + theme_cowplot() + facet_wrap(.~gene, nrow = 3) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "Larp1")), method = "wilcox.test") + ylab("Reporter Transcripts\nin Neurite") + guides(fill = FALSE)  + EnvStats::stat_n_text(y.pos = -50) + scale_x_discrete(limits = c("NC1",  "Larp1"))


Larp3top_summary <- Larp3top_filt %>% 
  group_by(gene,siRNA,image,cell,Cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene,siRNA,image, cell,Cell, N_thres_Total) %>% 
  group_by(gene,siRNA,image,Cell) %>% 
  mutate(Cell =as.numeric(substr(Cell,6,6)), Cell = ifelse(Cell %%2 == 0, Cell-1,Cell)) %>% 
  spread(key = cell, value = N_thres_Total) %>%
  mutate(neurite = ifelse(is.na(neurite), 0, neurite)) %>% 
  mutate(n_s_thresh = neurite/soma) %>% 
  select(gene, siRNA,image, n_s_thresh) %>% 
  ungroup() %>% left_join(., Larp3top_filt %>% group_by(gene,siRNA,image,cell,Cell) %>% summarize(N_thres_Total = n()) %>% ungroup() %>% select(gene,siRNA, image, cell, N_thres_Total))

Larp3top_summary %>% select(-N_thres_Total) %>% unique() %>% filter(cell == "soma", n_s_thresh < 1, !(gene == "FF" & n_s_thresh > 0.2)) %>% ggplot(aes(x = siRNA, y = n_s_thresh))   + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA)  + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "Larp1")), method = "wilcox.test") + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~factor(gene, levels = c("FF","RPL7", "RPL7mut", "RPS28", "RPS28mut")), nrow = 1) + EnvStats::stat_n_text(y.pos = -0.02) + coord_cartesian(ylim = c(-0.04,0.75)) + scale_fill_manual(values = c("#808080","#D0512E", "#D0512E", "#6e508d","#6e508d")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + theme(strip.background = element_rect(color = "white", fill = "white")) + theme(text = element_text(size=15), axis.text = element_text(size = 15)) 

Larp3top_summary %>% select(-N_thres_Total) %>% unique() %>% filter(cell == "soma", n_s_thresh < 1, !(gene == "FF" & n_s_thresh > 0.2)) %>% ggplot(aes(x = gene, y = n_s_thresh))  + geom_boxplot(aes(fill = gene,alpha = gene),outlier.shape = NA) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"), c("RPL7", "RPL7mut"), c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(0.36,0.42,0.5,0.58,0.3,0.45)) + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA, nrow = 2, scales = "free_y") + EnvStats::stat_n_text() + scale_fill_manual(values = c("#808080","#D0512E", "#D0512E", "#6e508d","#6e508d")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + theme(strip.background = element_rect(color = "white", fill = "white")) + theme(text = element_text(size=15), axis.text = element_text(size = 15)) + coord_cartesian(ylim = c(-0.12,0.70))

Larp3top_summary %>% select(-N_thres_Total) %>% unique() %>% filter(cell == "soma", n_s_thresh < 1, !(gene == "FF" & n_s_thresh > 0.2), gene %in% c("RPL7", "RPS28")) %>% ggplot(aes(x = siRNA, y = n_s_thresh)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA)  + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "Larp1")), method = "wilcox.test", label.y = c(0.175,0.175), label = "p.signif", size = 7, hide.ns = TRUE, vjust = 0.5) + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~factor(gene, levels = c("RPL7", "RPS28"), labels = c("RPL7\n3'TOP","RPS28\n3'TOP")), nrow = 1) + EnvStats::stat_n_text(y.pos = -0.01, size = 5) + coord_cartesian(ylim = c(-0.02,0.2)) + scale_fill_manual(values = c("#D0512E","#6e508d")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + theme(strip.background = element_rect(color = "white", fill = "white")) + theme(text = element_text(size=18), axis.text = element_text(size = 16)) + scale_x_discrete(limits = c("NC1", "Larp1"), labels = c("NC", "Larp1"))

Larp3top_summary %>% select(-N_thres_Total) %>% unique() %>% filter(cell == "soma", n_s_thresh < 1, !(gene == "FF" & n_s_thresh > 0.2), !(gene == "RPL7mut" & siRNA == "Larp1" & n_s_thresh > 0.2), gene %in% c("FF", "RPL7mut", "RPS28mut")) %>% ggplot(aes(x = siRNA, y = n_s_thresh)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA)  + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "Larp1")), method = "wilcox.test", label.y = 0.2, size = 7, label = "p.signif", vjust = 0.5, hide.ns = TRUE) + labs(x = "", y = "Reporter Transcripts\nin Neurite/Soma") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~factor(gene, levels = c("FF","RPL7mut", "RPS28mut"), labels = c("Firefly","RPL7mut\n3'TOP","RPS28mut\n3'TOP")), nrow = 1) + EnvStats::stat_n_text(y.pos = -0.01, size = 5) + coord_cartesian(ylim = c(-0.02,0.25)) + scale_fill_manual(values = c("#808080","#D0512E","#6e508d")) + scale_alpha_manual(values = c(1,0.5,0.5)) + theme(strip.background = element_rect(color = "white", fill = "white")) + theme(text = element_text(size=18), axis.text = element_text(size = 16)) + scale_x_discrete(limits = c("NC1", "Larp1"), labels = c("NC", "Larp1"))

```





