---
title: "C2bbe1 Larp FISH"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr)
library(cowplot)
```

## Round 1!
### RPL7 and its mutant were plated at high confluency on glass for 7 days of differentiation. siRNAs were transfected on day -2. cells were prepped for imaging at the end of the 7 day differentiation.


```{r, all spot tidy data}
all_spot_bbe1 <- as_tibble(read.csv("21.06.30_C2bbe1LarpFISH/Results/_FISH-QUANT__all_spots_210702.txt", header = TRUE, skip = 13, sep = "\t"))

all_spot_bbe12 <- as_tibble(read.csv("21.07.03_moreC2bbe1/Results/_FISH-QUANT__all_spots_210703.txt", header = TRUE, skip = 13, sep = "\t"))

##fix file names
all_spot_bbe1 <- rbind(all_spot_bbe1, all_spot_bbe12) %>% mutate(File = ifelse(startsWith(substr(File, 8, nchar(File)-10), prefix = "7d_"), substr(File, 11, nchar(File)-10), substr(File, 8, nchar(File)-10)))  

all_spot_bbe1 <- all_spot_bbe1 %>% separate(File, into = c("gene", "siRNA", "image"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything()) %>% mutate(siRNA = ifelse(siRNA == "none", siRNA, toupper(siRNA)))

```

```{r, all spot filter}
all_spot_bbe1 %>% select(gene,siRNA,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
all_spot_bbe1  %>% select(gene,siRNA,cell, SigmaX, SigmaZ, AMP, INT_filt, INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
all_spot_bbe1 %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(500,3500)  + geom_hline(yintercept = 1500)

all_spot_bbe1 %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(200,1200)  + geom_hline(yintercept = 775)

all_spot_bbe1 %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

all_spot_bbe1 %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
bbe1_filt <- all_spot_bbe1 %>% filter(as.numeric(INT_filt) > 1300, as.numeric(INT_raw) < 4000 ) #, as.numeric(BGD) > 750, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
bbe1_filt %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% filter(siRNA != "none") %>% ggplot(aes(x = siRNA, y = numspots, fill = siRNA)) + geom_boxplot() + theme_cowplot() + facet_wrap(.~gene, nrow = 3) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("NC1", "LARP1"), c("NC1", "LARP6"),c("NC1", "LARP7"), c("NC1", "SSB")), method = "wilcox.test") + scale_x_discrete(limits = c("NC1", "SSB", "LARP1", "LARP6", "LARP7"))

med_line <- bbe1_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-2000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

bbe1_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-2000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040")) + scale_alpha_manual(values = c(1,1,0.5))

#RPS28 color = "#b82080"

med_line_dat <- bbe1_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-2000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(med = median(Position_In_Z, na.rm = TRUE))

bbe1_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-2000) / 1000)) %>% filter(siRNA != "none") %>% left_join(., med_line_dat, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "LARP1"), c("NC1", "LARP6"),c("NC1", "LARP7"), c("NC1", "SSB")),label.y = c(6,7,8,5), method = "wilcox.test") + labs(x = "", y = "Position in Z (um)") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + geom_hline(aes(yintercept = med), linetype = "dashed") + scale_x_discrete(limits = c("NC1", "SSB", "LARP1", "LARP6", "LARP7"))  + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040")) + scale_alpha_manual(values = c(1,1,0.5)) + EnvStats::stat_n_text(y.pos = -2) + coord_cartesian(ylim = c(-2.5,8.5))

med_line_dat <- bbe1_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-2000) / 1000)) %>% filter(gene == "FF") %>% group_by(gene,siRNA) %>% summarise(med = median(Position_In_Z, na.rm = TRUE))

bbe1_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-2000) / 1000)) %>% filter(siRNA != "none") %>% left_join(., med_line_dat, by = "siRNA") %>% ggplot(aes(x = gene.x, y = Position_In_Z)) + geom_violin(aes(fill = gene.x, alpha = gene.x)) + geom_boxplot(aes(fill = gene.x, alpha = gene.x), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut")),label.y = c(6,7,8), method = "wilcox.test") + labs(x = "", y = "Position in Z (um)") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA, nrow = 3) + geom_hline(aes(yintercept = med), linetype = "dashed")   + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040")) + scale_alpha_manual(values = c(1,1,0.5)) + EnvStats::stat_n_text(y.pos = -2) + coord_cartesian(ylim = c(-2.5,8.5))

```


## Round 2!
## This time a little different... 
### RPS28 and its mutant were dox induced plated on glass and siRNA transfected all on the first day of differentiation, cells were plated and transfected at high conlfluency then differentiated for 7 days. 
#however, I will admit, these didnt go down as confluent as I had hoped....

```{r, 28dat}
all_spot_28<- as_tibble(read.csv("21.07.12C2bbe128/Results/_FISH-QUANT__all_spots_210713.txt", header = TRUE, skip = 13, sep = "\t"))

all_spot_28 <- all_spot_28 %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

```

```{r, 28 spot filter}
all_spot_28 %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-group,-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
all_spot_28  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, AMP, INT_filt, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
all_spot_28 %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(200,1500)  + geom_hline(yintercept = 500)

all_spot_28 %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(50,400)  + geom_hline(yintercept = 275)

all_spot_28 %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

all_spot_28 %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
filt28 <- all_spot_28 %>% filter(as.numeric(INT_raw) > 500, as.numeric(INT_raw) < 2000, as.numeric(BGD) < 275) #, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
filt28 %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% filter(siRNA != "none") %>% ggplot(aes(x = siRNA, y = numspots, fill = siRNA)) + geom_boxplot() + theme_cowplot() + facet_wrap(.~gene, nrow = 3) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("NC1", "LARP1"), c("NC1", "LARP6"),c("NC1", "LARP7"), c("NC1", "SSB")), method = "wilcox.test") + scale_x_discrete(limits = c("NC1", "SSB", "LARP1", "LARP6", "LARP7")) + guides(fill = FALSE)

filt28 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene != "Lox") %>% ggplot(aes(x= image, y = Position_In_Z)) + geom_boxplot() + theme_cowplot() + facet_grid(siRNA~gene) + coord_cartesian(ylim = c(-0,5))


med_line <- filt28 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

#filter(!(gene == "RPS28" & image == "03"), !(gene == "RPS28mut" & image == "02"))

filt28 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5))

#oh boy....

med_line_dat <- filt28 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(med = median(Position_In_Z, na.rm = TRUE))

filt28 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA != "none") %>% left_join(., med_line_dat, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "LARP1"), c("NC1", "LARP6"),c("NC1", "LARP7"), c("NC1", "SSB")), label.y = c(7,8,9,6), method = "wilcox.test") + labs(x = "", y = "Position in Z (um)") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + geom_hline(aes(yintercept = med), linetype = "dashed") + scale_x_discrete(limits = c("NC1", "SSB", "LARP1", "LARP6", "LARP7")) + scale_fill_manual(values = c("#808080","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5)) + EnvStats::stat_n_text(y.pos = -2) + coord_cartesian(ylim = c(-2.5,10))

```

## Round 3!
## same as last time... 
### RPL7 and its mutant were dox induced plated on glass and siRNA transfected all on the first day of differentiation, cells were plated and transfected at high conlfluency then differentiated for 7 days. 
#however, I will admit, these also didnt go down as confluent as I had hoped....

```{r, }
all_spot_7<- as_tibble(read.csv("21.07.20_C2bbe1RP7FISHLarp/Results/_FISH-QUANT__all_spots_210720.txt", header = TRUE, skip = 13, sep = "\t"))

all_spot_7 <- all_spot_7 %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

```

```{r, }
all_spot_7 %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-group,-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
all_spot_7  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, AMP, INT_filt, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
all_spot_7 %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(400,2000)  + geom_hline(yintercept = 1400)

all_spot_7 %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(50,1000)  + geom_hline(yintercept = 575)

all_spot_7 %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

all_spot_7 %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
filt7 <- all_spot_7 %>% filter(as.numeric(INT_raw) > 1400, as.numeric(INT_raw) < 4000, as.numeric(BGD) < 500) #, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
filt7 %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot() + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut")), method = "wilcox.test") + guides(fill = FALSE)

#image 03 is weird
filt7 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% ggplot(aes(x= image, y = Position_In_Z)) + geom_boxplot() + theme_cowplot() + facet_wrap(.~gene)

med_line <- filt7 %>% filter(!(gene == "RPL7" & image == "03")) %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

filt7 %>% filter(gene != "Lox", !(gene == "RPL7" & image == "03")) %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040")) + scale_alpha_manual(values = c(1,1,0.5))

# take more pics??
# cant =[

```

## Round 4!
## 10 days of differentiation!
### RPS28 and its mutant were dox induced plated on glass and siRNA transfected all on the first day of differentiation, cells were plated and transfected at high conlfluency then differentiated for 10 days. 
```{r, }
spot10d_28 <- as_tibble(read.csv("21.07.30_10dRPS28/Results/_FISH-QUANT__all_spots_210731.txt", header = TRUE, skip = 13, sep = "\t"))
spot10d_28_2 <- as_tibble(read.csv("21.07.30_10dRPS28/Results/_FISH-QUANT__all_spots_210803.txt", header = TRUE, skip = 13, sep = "\t"))

spot10d_28 <- rbind(spot10d_28,spot10d_28_2) %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

```

```{r, }
spot10d_28 %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-group,-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
spot10d_28  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, AMP, INT_filt, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
spot10d_28 %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(250,1250)  + geom_hline(yintercept = 550)

spot10d_28 %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(50,500)  + geom_hline(yintercept = 400)

spot10d_28 %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

spot10d_28 %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
filt10d_28 <- spot10d_28 %>% filter(as.numeric(INT_raw) > 550, as.numeric(INT_raw) < 4000) #, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
filt10d_28 %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), label.y = c(550,600,650), method = "wilcox.test") + guides(fill = FALSE) + coord_cartesian(ylim = c(0,750))

#image 1 for RPS28 is weird.
filt10d_28 %>% filter(gene != "Lox") %>% ggplot(aes(x = image, y = Pos_Z)) + geom_boxplot() + facet_grid(siRNA~gene) + theme_cowplot() + coord_cartesian(ylim = c(2500,8000)) 

med_line <- filt10d_28 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

filt10d_28 %>% filter(!(gene == "RPS28" & image == "01" & siRNA == "NC1"), gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5))

med_lines <- filt10d_28 %>% filter(!(gene == "RPS28" & image == "01" & siRNA == "NC1"), gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z,na.rm = TRUE)) %>% filter(gene == "FF")

filt10d_28 %>% filter(!(gene == "RPS28" & image == "01" & siRNA == "NC1"), gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "siRNA") %>% ggplot(aes(x = gene.x, y = Position_In_Z)) + geom_violin(aes(fill = gene.x, alpha = gene.x))+ geom_boxplot(aes(fill = gene.x, alpha = gene.x), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")),label.y = c(6.5,7.5,8.5), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA, nrow = 3) + geom_hline(aes(yintercept = medline), linetype = "dashed") + scale_fill_manual(values = c("#808080","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5)) + coord_cartesian(ylim = c(-2.5,10)) + EnvStats::stat_n_text(y.pos = -2)

#list of weird images:
# filter(!(gene == "RPS28" & image == "01" & siRNA == "NC1"),
#        !(gene == "RPS28" & image == "03" & siRNA == "SSB"),
#        !(gene == "RPS28" & image == "03" & siRNA == "LARP7"),
#        !(gene == "FF" & image == "03" & siRNA == "LARP7"),
#        !(gene == "RPS28mut" & image == "02" & siRNA == "LARP1"),
#        !(gene == "RPS28mut" & image == "01" & siRNA == "SSB"),
#        !(gene == "RPS28mut" & image == "03" & siRNA == "SSB"),
#        !(gene == "RPS28mut" & image == "03" & siRNA == "LARP7"))

med_lines <- filt10d_28 %>% filter(!(gene == "RPS28" & image == "01" & siRNA == "NC1"), gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

filt10d_28 %>% filter(!(gene == "RPS28" & image == "01" & siRNA == "NC1"), gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "SSB"), c("NC1", "LARP1"),c("NC1", "LARP6"), c("NC1", "LARP7")), label.y = c(5.5, 6.5, 7.5, 8.5), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + geom_hline(aes(yintercept = medline), linetype = "dashed") + scale_fill_manual(values = c("#808080","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5)) + scale_x_discrete(limits = c("NC1", "SSB", "LARP1", "LARP6", "LARP7")) + coord_cartesian(ylim = c(-2.5,10)) 

#yay!

```

## Round 5!
## 10 days of differentiation!
### RPL7 and its mutant were dox induced plated on glass and siRNA transfected all on the first day of differentiation, cells were plated and transfected at high conlfluency then differentiated for 10 days. 
```{r, }
spot10d_7 <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.08.02_10dRPL7/Results/_FISH-QUANT__all_spots_210803.txt", header = TRUE, skip = 13, sep = "\t"))

spot10d_7_2 <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.08.02_10dRPL7/Results/_FISH-QUANT__all_spots_210804.txt", header = TRUE, skip = 13, sep = "\t"))

spot10d_7 <- rbind(spot10d_7,spot10d_7_2) %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

```

```{r,}
spot10d_7 %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-group,-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
spot10d_7  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, AMP, INT_filt, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
spot10d_7 %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(500,2000)  + geom_hline(yintercept = 1250)

spot10d_7 %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(300,1500)  + geom_hline(yintercept = 400)

spot10d_7 %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

spot10d_7 %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
filt10d_7 <- spot10d_7 %>% filter(TH_fit == 1, as.numeric(INT_raw) > 1250, as.numeric(INT_raw) < 4000) #, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
filt10d_7 %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut")), method = "wilcox.test") + guides(fill = FALSE)

#image 1 for RPS28 is weird.
filt10d_7 %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% ggplot(aes(x = image, y = Position_In_Z)) + geom_boxplot() + facet_grid(siRNA~gene) + theme_cowplot() + coord_cartesian(ylim = c(-2,5))

med_line <- filt10d_7 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

filt10d_7 %>% filter(!(gene == "RPL7" & image == "02" & siRNA == "NC1"),!(gene == "RPL7mut" & image == "04" & siRNA == "NC1"), gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040")) + scale_alpha_manual(values = c(1,1,0.5))

#list of weird images:
# filter(!(gene == "RPL7" & image == "02" & siRNA == "NC1"),
#        !(gene == "RPL7" & image == "02" & siRNA == "none"),
#        !(gene == "RPL7mut" & image == "04 "& siRNA == "NC1"),
#        !(gene == "RPL7mut" & image == "03 "& siRNA == "LARP1"),
#        !(gene == "RPL7mut" & image == "03 "& siRNA == "LARP6"))

med_lines <- filt10d_7  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

filt10d_7 %>% filter(!(gene == "RPL7" & siRNA == "NC1" & image == "02"), gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "SSB"), c("NC1", "LARP1"),c("NC1", "LARP6"), c("NC1", "LARP7")), label.y = c(6,7,8,9), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040")) + scale_alpha_manual(values = c(1,1,0.5)) + scale_x_discrete(limits = c("none","NC1", "SSB", "LARP1", "LARP6", "LARP7")) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,12))



```


## now by siRNA 

```{r, }
p <- bind_rows(list("Day-2" = bbe1_filt, "Day10_28" = filt10d_28, "Day10_7" = filt10d_7), .id = "trsfx_day") %>% 
  filter(siRNA %in% c("SSB","LARP6", "LARP7", "NC1"), 
         gene != "Lox",
         !(gene == "RPL7" & siRNA == "NC1" & image == "02" & trsfx_day == "Day10_7"),
         !(gene == "RPL7mut" & image == "04" & siRNA == "NC1" & trsfx_day == "Day10_7"),
         !(gene == "RPS28" & image == "01" & siRNA == "NC1" & trsfx_day == "Day10_28")) %>%
  mutate(Position_In_Z = ifelse(trsfx_day == "Day-2", ((as.numeric(Pos_Z)-2000) / 1000), ((as.numeric(Pos_Z)-3000) / 1000))) 

med_lines <- p %>% filter(gene == "FF") %>% group_by(gene,trsfx_day,siRNA) %>% summarise(medlines = median(Position_In_Z, na.rm = TRUE))

p %>% left_join(.,med_lines) %>% 
  ggplot(aes(x = gene, y = Position_In_Z)) + 
  geom_boxplot(aes(fill = gene, alpha = gene),outlier.shape = NA) + 
  theme_cowplot() +
  stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"), c("RPL7", "RPL7mut")), 
                      #c("FF", "RPS28"), c("FF", "RPS28mut"), c("RPS28", "RPS28mut")), 
                     label.y = c(4,5,3.5), 
                     method = "wilcox.test") +
  facet_grid(siRNA~factor(trsfx_day, levels = c("Day-2", "Day10_7", "Day10_28")), scales = "free_x") +
  coord_cartesian(ylim = c(-2,8)) +
  geom_hline(aes(yintercept = medlines), linetype = "dashed") + 
  scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) +
  scale_alpha_manual(values = c(1,1,0.5,1,0.5)) +
  guides(fill = FALSE, alpha = FALSE)
  
```


## Round 6!
## 7 days of differentiation!
### both RPs and mutants were dox induced plated on glass and siRNA transfected all on the first day of differentiation, cells were plated and transfected at high conlfluency then differentiated for 7 days. 
### Only Larp1, Larp6, NC1 and no siRNA were tested 
```{r, }
R6_spots <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.08.24_7dLarpFISH/Results/_FISH-QUANT__all_spots_210825.txt", header = TRUE, skip = 13, sep = "\t"))

R6_spots_2 <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.08.24_7dLarpFISH/Results/_FISH-QUANT__all_spots_210826.txt", header = TRUE, skip = 13, sep = "\t"))

R6_spots <- rbind(R6_spots, R6_spots_2) %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

```

```{r,}
R6_spots %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-group,-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
R6_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, AMP, INT_filt, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
#INTRAW
R6_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,1000) + geom_hline(yintercept = 400)

R6_spots %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(100,1000)  + geom_hline(yintercept = 450)

R6_spots %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(0,500)  + geom_hline(yintercept = 275)

R6_spots %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

R6_spots %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
R6_spots_filt <- R6_spots %>% filter(TH_fit == 1, as.numeric(INT_raw) > 450, as.numeric(INT_raw) < 1500) #, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
R6_spots_filt %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + guides(fill = FALSE)

#image 1 for RPS28 is weird.
R6_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% ggplot(aes(x = image, y = Position_In_Z)) + geom_boxplot()  + facet_grid(siRNA~gene) + theme_cowplot() + coord_cartesian(ylim = c(0,6))

R6_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000), cell = as.character(cell)) %>% group_by(gene,siRNA,image,cell) %>% summarize(mean_PositioninZ = mean(Position_In_Z, na.rm = TRUE)) %>% ggplot(aes(x = image, y = mean_PositioninZ)) + geom_boxplot() + geom_point(aes(col = cell, shape = cell), size = 4, position = "jitter") + facet_grid(siRNA~gene, scales = "free_y") + theme_cowplot() + scale_shape_manual(values = c(0,1,2,3,4,7,10)) + coord_cartesian(ylim = c(2,4))

R6_spots_filt2 <- R6_spots_filt %>% 
  filter(!(gene == "RPL7" & image == "01" & siRNA == "NC1" & cell == 5),
         !(gene == "RPL7" & image == "02" & siRNA == "NC1" & cell %in% c(1,3,5)),
         !(gene == "RPL7" & image == "04" & siRNA == "NC1" & cell == 6),
         !(gene == "FF" & image == "01" & siRNA == "NC1" & cell %in% c(2,3)),
         !(gene == "FF" & image == "02" & siRNA == "NC1" & cell %in% c(2,3)),
         !(gene == "FF" & image == "03" & siRNA == "NC1"),
         !(gene == "FF" & image == "05" & siRNA == "NC1" & cell %in% c(2,3,4,5)),
         !(gene == "RPS28" & image == "01" & siRNA == "NC1" & cell == 1),
         !(gene == "RPS28" & image == "02" & siRNA == "NC1" & cell %in% c(2,4)),
         !(gene == "RPS28" & image == "03" & siRNA == "NC1" & cell %in% c(1,2,3,4)),
         !(gene == "RPS28" & image == "04" & siRNA == "NC1"),
         !(gene == "RPS28mut" & image == "02" & siRNA == "NC1" & cell == 4),
         !(gene == "RPS28mut" & image == "04" & siRNA == "NC1" & cell == 3),
         !(gene == "RPS28mut" & image == "03" & siRNA == "NC1" & cell == 6),
         !(gene == "FF" & image == "02" & siRNA == "none" & cell %in% c(1,2,5)),
         !(gene == "RPL7" & image == "01" & siRNA == "none" & cell == 5),
         !(gene == "RPS28" & image == "02" & siRNA == "none" & cell %in% c(1,5,6)),
         !(gene == "RPL7mut" & image == "01" & siRNA == "none" & cell %in% c(1,4)),
         !(gene == "RPL7mut" & image == "02" & siRNA == "none"),
         !(gene == "RPL7mut" & image == "03" & siRNA == "none" & cell %in% c(1,6)),
         !(gene == "RPS28mut" & image == "01" & siRNA == "none"),
         !(gene == "RPS28" & image == "02" & siRNA == "LARP1"),
         !(gene == "RPS28mut" & image == "01" & siRNA == "LARP1"),
         !(gene == "FF" & image == "03" & siRNA == "LARP6"),
         !(gene == "RPL7" & image == "03" & siRNA == "LARP6"),
         !(gene == "RPL7" & image == "04" & siRNA == "LARP6" & cell == 2),
         !(gene == "RPL7mut" & image == "01" & siRNA == "LARP6" & cell == 5),
         !(gene == "RPL7mut" & image == "02" & siRNA == "LARP6"),
         !(gene == "RPL7mut" & image == "03" & siRNA == "LARP6" & cell %in% c(1,2)),
         !(gene == "RPS28" & image == "02" & siRNA == "LARP6" & cell == 1),
         !(gene == "RPS28" & image == "03" & siRNA == "LARP6" & cell == 2),
         !(gene == "RPS28mut" & image == "03" & siRNA == "LARP6" & cell %in% c(2,6)),
         !(gene == "RPS28mut" & image == "01" & siRNA == "LARP6" & cell == 3),
         !(gene == "RPS28mut" & image == "02" & siRNA == "LARP6" & cell == 4))


med_line <- R6_spots_filt2 %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

R6_spots_filt2 %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))

med_lines <- R6_spots_filt2  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R6_spots_filt2 %>% filter(gene != "Lox", siRNA != "none") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "LARP1"),c("NC1", "LARP6")), label.y = c(6,7,8,9), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + scale_x_discrete(limits = c("NC1", "LARP1", "LARP6")) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,10.5))

med_lines <- R6_spots_filt2  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R6_spots_filt2 %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "siRNA") %>% ggplot(aes(x = gene.x, y = Position_In_Z)) + geom_violin(aes(fill = gene.x, alpha = gene.x)) + geom_boxplot(aes(fill = gene.x, alpha = gene.x), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(7.5,8.5,7,9.5,10.5,7)) + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA, nrow = 4) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,12))

```

## Round 7!
## 7 days of differentiation!
### both RPs and mutants were dox induced plated on glass and siRNA transfected all on the first day of differentiation, cells were plated and transfected at high conlfluency then differentiated for 7 days. 

```{r, }
R7_spots <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.09.02_C2bbe1FISH/Results/_FISH-QUANT__all_spots_210907.txt", header = TRUE, skip = 13, sep = "\t"))

R7_spots <- R7_spots %>% filter(!grepl(File,pattern = "Net1"), !grepl(File, pattern = "BC200")) %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

```

```{r,}
R7_spots %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-group,-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
R7_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, AMP, INT_filt, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
#INTRAW
R7_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000) + geom_hline(yintercept = 1000)

R7_spots %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(400,2000)  + geom_hline(yintercept = 1000)

R7_spots %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(200,1000)  + geom_hline(yintercept = 675)

R7_spots %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

R7_spots %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
R7_spots_filt <- R7_spots %>% filter(TH_fit == 1, as.numeric(INT_raw) > 1000, as.numeric(INT_raw) < 3500) #, as.numeric(Pos_Z) > 450, as.numeric(Pos_Z) < 10000)
```

```{r, }
R7_spots_filt %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + guides(fill = FALSE)

#image 1 for RPS28 is weird.
R7_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% ggplot(aes(x = image, y = Position_In_Z)) + geom_boxplot()  + facet_grid(siRNA~gene) + theme_cowplot() + coord_cartesian(ylim = c(0,6))

R7_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000), cell = as.character(cell)) %>% group_by(gene,siRNA,image,cell) %>% summarize(mean_PositioninZ = mean(Position_In_Z, na.rm = TRUE)) %>% ggplot(aes(x = image, y = mean_PositioninZ)) + geom_boxplot() + geom_point(aes(col = cell, shape = cell), size = 4, position = "jitter") + facet_grid(siRNA~gene, scales = "free_y") + theme_cowplot() + scale_shape_manual(values = c(0,1,2,3,4,7,10)) + coord_cartesian(ylim = c(2,4))

R7_spots_filt2 <- R7_spots_filt %>% 
  filter(!(gene == "RPL7" & image == "01" & siRNA == "NC1" & cell == 5),
         !(gene == "RPL7" & image == "02" & siRNA == "NC1" & cell %in% c(1,3,5)),
         !(gene == "RPL7" & image == "04" & siRNA == "NC1" & cell == 6),
         !(gene == "FF" & image == "01" & siRNA == "NC1" & cell %in% c(2,3)),
         !(gene == "FF" & image == "02" & siRNA == "NC1" & cell %in% c(2,3)),
         !(gene == "FF" & image == "03" & siRNA == "NC1"),
         !(gene == "FF" & image == "05" & siRNA == "NC1" & cell %in% c(2,3,4,5)),
         !(gene == "RPS28" & image == "01" & siRNA == "NC1" & cell == 1),
         !(gene == "RPS28" & image == "02" & siRNA == "NC1" & cell %in% c(2,4)),
         !(gene == "RPS28" & image == "03" & siRNA == "NC1" & cell %in% c(1,2,3,4)),
         !(gene == "RPS28" & image == "04" & siRNA == "NC1"),
         !(gene == "RPS28mut" & image == "02" & siRNA == "NC1" & cell == 4),
         !(gene == "RPS28mut" & image == "04" & siRNA == "NC1" & cell == 3),
         !(gene == "RPS28mut" & image == "03" & siRNA == "NC1" & cell == 6),
         !(gene == "FF" & image == "02" & siRNA == "none" & cell %in% c(1,2,5)),
         !(gene == "RPL7" & image == "01" & siRNA == "none" & cell == 5),
         !(gene == "RPS28" & image == "02" & siRNA == "none" & cell %in% c(1,5,6)),
         !(gene == "RPL7mut" & image == "01" & siRNA == "none" & cell %in% c(1,4)),
         !(gene == "RPL7mut" & image == "02" & siRNA == "none"),
         !(gene == "RPL7mut" & image == "03" & siRNA == "none" & cell %in% c(1,6)),
         !(gene == "RPS28mut" & image == "01" & siRNA == "none"),
         !(gene == "RPS28" & image == "02" & siRNA == "LARP1"),
         !(gene == "RPS28mut" & image == "01" & siRNA == "LARP1"),
         !(gene == "FF" & image == "03" & siRNA == "LARP6"),
         !(gene == "RPL7" & image == "03" & siRNA == "LARP6"),
         !(gene == "RPL7" & image == "04" & siRNA == "LARP6" & cell == 2),
         !(gene == "RPL7mut" & image == "01" & siRNA == "LARP6" & cell == 5),
         !(gene == "RPL7mut" & image == "02" & siRNA == "LARP6"),
         !(gene == "RPL7mut" & image == "03" & siRNA == "LARP6" & cell %in% c(1,2)),
         !(gene == "RPS28" & image == "02" & siRNA == "LARP6" & cell == 1),
         !(gene == "RPS28" & image == "03" & siRNA == "LARP6" & cell == 2),
         !(gene == "RPS28mut" & image == "03" & siRNA == "LARP6" & cell %in% c(2,6)),
         !(gene == "RPS28mut" & image == "01" & siRNA == "LARP6" & cell == 3),
         !(gene == "RPS28mut" & image == "02" & siRNA == "LARP6" & cell == 4))


med_line <- R7_spots_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

R7_spots_filt %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))

med_lines <- R7_spots_filt  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R7_spots_filt %>% filter(gene != "Lox", siRNA != "none") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "SSB"),c("NC1", "LARP1"),c("NC1", "LARP6"),c("NC1", "LARP7")), label.y = c(6,7,8,9), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + scale_x_discrete(limits = c("NC1", "SSB","LARP1", "LARP6","LARP7")) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,10.5))

med_lines <- R7_spots_filt  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R7_spots_filt %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "siRNA") %>% ggplot(aes(x = gene.x, y = Position_In_Z)) + geom_violin(aes(fill = gene.x, alpha = gene.x)) + geom_boxplot(aes(fill = gene.x, alpha = gene.x), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(7.5,8.5,7,9.5,10.5,7)) + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA, nrow = 4) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,12))

```

## Round 8!
## 7 days of differentiation!
### both RPs and mutants were dox induced plated on glass and siRNA transfected all on fifth day of differentiation, cells were plated at high conlfluency then differentiated for 7 days. Transfection on day -2 (48hours with siRNAs)
### New LARP1 siRNAs!

```{r, }
R8_spots <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.09.17_7d-2Larp/Results/_FISH-QUANT__all_spots_210919.txt", header = TRUE, skip = 13, sep = "\t"))

R8_spots <- R8_spots %>% filter(!grepl(File,pattern = "BC1")) %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

```

```{r,}
R8_spots %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% gather(-group,-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free", nrow =2) + theme_cowplot()

#only Int_raw is different
R8_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, SigmaX, SigmaZ, AMP, INT_filt, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(0,2000)

##a closer look with each condition.
#INTRAW
R8_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(400,2500) + geom_hline(yintercept = 1250)

R8_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, BGD) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(200,1000) + geom_hline(yintercept = 500)

R8_spots %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(400,2500)  + geom_hline(yintercept = 1250)

R8_spots %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(200,1000)  + geom_hline(yintercept = 500)

R8_spots %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

R8_spots %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
R8_spots_filt <- R8_spots %>% filter(TH_fit == 1, as.numeric(INT_raw) > 1000, as.numeric(INT_raw) < 4000)#,  as.numeric(BGD) < 500), as.numeric(Pos_Z) < 10000)
```

```{r, }
R8_spots_filt %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + guides(fill = FALSE)

#image 1 for RPS28 is weird.
R8_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% ggplot(aes(x = image, y = Position_In_Z)) + geom_boxplot()  + facet_grid(siRNA~gene) + theme_cowplot() + coord_cartesian(ylim = c(0,6))

R8_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000), cell = as.character(cell)) %>% group_by(gene,siRNA,image,cell) %>% summarize(mean_PositioninZ = mean(Position_In_Z, na.rm = TRUE)) %>% ggplot(aes(x = image, y = mean_PositioninZ)) + geom_boxplot() + geom_point(aes(col = cell, shape = cell), size = 4, position = "jitter") + facet_grid(siRNA~gene, scales = "free_y") + theme_cowplot() + scale_shape_manual(values = c(0,1,2,3,4,7,10)) + coord_cartesian(ylim = c(1,6))

R8_spots_filt2 <- R8_spots_filt %>% 
  filter(!(gene == "FF" & image == "01" & siRNA == "NC1"),
         !(gene == "RPL7" & image %in% c("01","02") & siRNA == "NC1"),
         !(gene == "RPL7mut" & image == "01" & siRNA == "NC1"),
         !(gene == "RPS28" & image %in% c("01","02") & siRNA == "NC1"))


med_line <- R8_spots_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

R8_spots_filt %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))

med_lines <- R8_spots_filt  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R8_spots_filt %>% filter(gene != "Lox", siRNA != "none") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "SSB"),c("NC1", "LARP1"),c("NC1", "LARP6"),c("NC1", "LARP7")), label.y = c(6,7,8,9), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + scale_x_discrete(limits = c("NC1", "SSB","LARP1", "LARP6","LARP7")) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,10.5))

med_lines <- R8_spots_filt  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R8_spots_filt %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "siRNA") %>% ggplot(aes(x = gene.x, y = Position_In_Z)) + geom_violin(aes(fill = gene.x, alpha = gene.x)) + geom_boxplot(aes(fill = gene.x, alpha = gene.x), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(7.5,8.5,7,9.5,10.5,7)) + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA, nrow = 4) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,12))

```

## Round 9!
## 7 days of differentiation!
### both RPs and mutants were dox induced plated on glass and siRNA transfected all on fifth day of differentiation, cells were plated at high conlfluency then differentiated for 7 days. Transfection on day -2 (48hours with siRNAs)
### New LARP1 siRNAs!

```{r, }
R9_spots <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.09.21_C2bbe1LARP-2d/Results/_FISH-QUANT__all_spots_210926.txt", header = TRUE, skip = 13, sep = "\t"))

R9_spots <- R9_spots %>% filter(!grepl(File,pattern = "BC1")) %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

R9_spots <- filter(R9_spots, gene != "BC1", gene != "BC200", !(gene == "FF" & siRNA == "none"))
```

```{r,}
#INTRAW
R9_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(200,1500) + geom_hline(yintercept = 700)

R9_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, BGD) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(200,1000) + geom_hline(yintercept = 500)

R9_spots %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(200,1500)  + geom_hline(yintercept = 700)

R9_spots %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(200,1000)  + geom_hline(yintercept = 500)

R9_spots %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

R9_spots %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
R9_spots_filt <- R9_spots %>% filter(TH_fit == 1, as.numeric(INT_raw) > 700, as.numeric(INT_raw) < 4000)#,  as.numeric(BGD) < 500), as.numeric(Pos_Z) < 10000)
```

```{r, }
R9_spots_filt %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + guides(fill = FALSE)

#image 1 for RPS28 is weird.
R9_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% ggplot(aes(x = image, y = Position_In_Z)) + geom_boxplot()  + facet_grid(siRNA~gene) + theme_cowplot() + coord_cartesian(ylim = c(0,6))

R9_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000), cell = as.character(cell)) %>% group_by(gene,siRNA,image,cell) %>% summarize(mean_PositioninZ = mean(Position_In_Z, na.rm = TRUE)) %>% ggplot(aes(x = image, y = mean_PositioninZ)) + geom_boxplot() + geom_point(aes(col = cell, shape = cell), size = 4, position = "jitter") + facet_grid(siRNA~gene, scales = "free_y") + theme_cowplot() + scale_shape_manual(values = c(0,1,2,3,4,7,10)) + coord_cartesian(ylim = c(1,6))

#!(gene == & image == & cell == )

med_line <- R9_spots_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

R9_spots_filt %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))

med_lines <- R9_spots_filt  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R9_spots_filt %>% filter(gene != "Lox", siRNA != "none") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "SSB"),c("NC1", "LARP1"),c("NC1", "LARP7")), label.y = c(6,7,8,9), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + scale_x_discrete(limits = c("NC1", "SSB","LARP1","LARP7")) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,10.5))

med_lines <- R9_spots_filt  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R9_spots_filt %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "siRNA") %>% ggplot(aes(x = gene.x, y = Position_In_Z)) + geom_violin(aes(fill = gene.x, alpha = gene.x)) + geom_boxplot(aes(fill = gene.x, alpha = gene.x), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(7.5,8.5,7,9.5,10.5,7)) + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA, nrow = 4) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,12))

```

## Round 10!
## 7 days of differentiation!
### both RPs and mutants were dox induced plated on glass and siRNA transfected all on fifth day of differentiation, cells were plated at high conlfluency then differentiated for 7 days. Transfection on day -2 (48hours with siRNAs)
### New LARP1 siRNAs!

```{r, }
R10_spots <- as_tibble(read.csv("/Users/raegoering/Documents/TaliaferroLab/IEC_FISH/21.09.27_C2bbe1LARP-2d/Results/_FISH-QUANT__all_spots_210928.txt", header = TRUE, skip = 13, sep = "\t"))

R10_spots <- R10_spots %>% filter(!grepl(File,pattern = "BC1")) %>% separate(File, into = c("C2bbe1","sd","gene", "siRNA", "image","stack"), sep = "_") %>%  mutate(cell = as.numeric(substr(Cell, 6, 6)), image = substr(image,1,2)) %>% select(gene, siRNA, image, cell, everything(), -C2bbe1, -sd, -stack, -Cell) 

R10_spots <- filter(R10_spots, gene != "BC1", gene != "BC200")

```

```{r,}
#INTRAW
R10_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, INT_raw) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(400,2500) + geom_hline(yintercept = 900)

R10_spots  %>% mutate(group = ifelse(gene == "Lox", "neg", "pos")) %>% select(group,gene,siRNA,cell, BGD) %>% gather(-group,-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = group, fill = group)) + geom_density(alpha = 0.5) + facet_wrap(.~param, scales = "free",nrow = 2) + theme_cowplot() + ylim(200,1000) + geom_hline(yintercept = 500)

R10_spots %>% select(gene,siRNA, cell,INT_raw) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot() + ylim(400,2500)  + geom_hline(yintercept = 900)

R10_spots %>% select(gene,siRNA,cell,BGD) %>% gather(-gene,-siRNA,-cell, key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha =0.5) + theme_cowplot() + ylim(200,1000)  + geom_hline(yintercept = 500)

R10_spots %>% select(gene,siRNA,cell,SigmaX) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()   + geom_hline(yintercept = 250)

R10_spots %>% select(gene,siRNA,cell,SigmaZ) %>% gather(-gene,-siRNA,-cell,key = "param", value = "value") %>% mutate(value = as.numeric(value)) %>% ggplot(aes(y=value, group = gene, fill = gene)) + geom_density(alpha = 0.5) + theme_cowplot()  + geom_hline(yintercept = 750)


#really limits spots.
R10_spots_filt <- R10_spots %>% filter(TH_fit == 1, as.numeric(INT_raw) > 1000, as.numeric(INT_raw) < 2000)#,  as.numeric(BGD) < 500), as.numeric(Pos_Z) < 10000)
```

```{r, }
R10_spots_filt %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + guides(fill = FALSE)

#image 1 for RPS28 is weird.
R10_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% ggplot(aes(x = image, y = Position_In_Z)) + geom_boxplot()  + facet_grid(siRNA~gene) + theme_cowplot() + coord_cartesian(ylim = c(0,6))

R10_spots_filt %>% filter(gene != "Lox") %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000), cell = as.character(cell)) %>% group_by(gene,siRNA,image,cell) %>% summarize(mean_PositioninZ = mean(Position_In_Z, na.rm = TRUE)) %>% ggplot(aes(x = image, y = mean_PositioninZ)) + geom_boxplot() + geom_point(aes(col = cell, shape = cell), size = 4, position = "jitter") + facet_grid(siRNA~gene, scales = "free_y") + theme_cowplot() + scale_shape_manual(values = c(0,1,2,3,4,7,10)) + coord_cartesian(ylim = c(0,4))

R10_spots_filt2 <- R10_spots_filt %>% 
  filter(!(gene == "FF" & siRNA == "NC1" & image == "02"),
         !(gene == "RPL28mut" & siRNA == "NC1" & image == "02"),
         !(gene == "RPL7mut" & siRNA == "none" & image == "01"),
         !(gene == "RPS28mut" & siRNA == "none" & image == "04"),
         #!(gene == "FF" & siRNA == "LARP1" & image == "01"),
         !(gene == "RPS28mut" & siRNA == "LARP1" & image %in% c("01", "02")),
         !(gene == "RPS28mut" & siRNA == "LARP6" & image == "03"))

med_line <- R10_spots_filt %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

R10_spots_filt %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))

med_lines <- R10_spots_filt  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(siRNA == "NC1") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R10_spots_filt %>% filter(gene != "Lox", siRNA != "none") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "gene") %>% ggplot(aes(x = siRNA.x, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene)) + geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "LARP1"),c("NC1", "LARP6")), label.y = c(6,7,8,9), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene, nrow = 3) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + scale_x_discrete(limits = c("NC1","LARP1", "LARP6")) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,10.5))

med_lines <- R10_spots_filt  %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% filter(gene == "FF") %>% group_by(gene,siRNA) %>% summarise(medline = median(Position_In_Z, na.rm = TRUE))

R10_spots_filt %>% filter(gene != "Lox") %>% group_by(gene,siRNA,image,cell) %>% mutate(Position_In_Z = ((as.numeric(Pos_Z)-3000) / 1000)) %>% left_join(., med_lines, by = "siRNA") %>% ggplot(aes(x = gene.x, y = Position_In_Z)) + geom_violin(aes(fill = gene.x, alpha = gene.x)) + geom_boxplot(aes(fill = gene.x, alpha = gene.x), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test", label.y = c(7.5,8.5,7,9.5,10.5,7)) + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA, nrow = 4) + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040","#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + geom_hline(aes(yintercept = medline), linetype = "dashed") + coord_cartesian(ylim = c(0,12))

```

# ALL -2 siRNA trsfx data!

```{r, }
m2Dat <- bind_rows(bbe1_filt, R8_spots_filt, R9_spots_filt, R10_spots_filt, .id = "round")

#remove first LARP1 siRNAs that didnt knock down at -2 days
m2Dat <- filter(m2Dat, !(siRNA == "LARP1" & round == 1))

m2Dat %>% group_by(gene,siRNA,image,cell, round) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + guides(fill = FALSE)

#try to normalize each imaging round using bottom 25% of cells
m2Dat_norm <- m2Dat %>% filter(gene != "Lox") %>% group_by(round) %>% summarise(minPosZ = quantile(as.numeric(Pos_Z),0.25)) %>% left_join(m2Dat) %>% mutate(Position_In_Z = (as.numeric(Pos_Z) - minPosZ +2000)/1000) 

m2Dat_norm %>% group_by(gene,siRNA,image,cell,round) %>% summarise(meanPosZ = median(Position_In_Z), na.rm = TRUE) %>% mutate(Rimg = paste(image,round,sep = "_")) %>% ggplot(aes(x = Rimg, y = meanPosZ, col = round)) + geom_boxplot() + geom_point(aes(shape = as.character(cell))) + facet_grid(gene~siRNA) + theme_cowplot()

#image 1 for RPS28 is weird.
m2Dat_norm %>% filter(gene != "Lox",gene == "FF") %>% group_by(gene,siRNA,image,cell,round) %>%  summarise(medPosZ = median(Position_In_Z,na.rm = TRUE) ) %>% mutate(Rimg = paste(round,image,sep = "_")) %>% ggplot(aes(x = Rimg, y = medPosZ,col = round)) + geom_boxplot() + geom_point(aes(shape = as.character(cell))) + facet_grid(gene~siRNA) + theme_cowplot() + coord_cartesian(ylim = c(0,6))


#m2Dat_norm2 <- filter(!(gene = & siRNA = & round = & image = ))


med_line <- m2Dat_norm %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

m2Dat_norm %>% filter(gene != "Lox") %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))


med_line <- m2Dat_norm %>% filter(gene == "FF") %>% group_by(siRNA) %>% summarise(med_line= median(Position_In_Z,na.rm = TRUE))

m2Dat_norm %>% filter(gene != "Lox") %>% left_join(.,med_line, by = "siRNA") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(aes(yintercept = med_line), linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))

med_line <- m2Dat_norm %>% filter(siRNA == "NC1") %>% group_by(gene) %>% summarise(med_line= median(Position_In_Z,na.rm = TRUE))

m2Dat_norm %>% filter(gene != "Lox") %>% left_join(.,med_line, by = "gene") %>% ggplot(aes(x = siRNA, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "none"), c("NC1", "SSB"), c("NC1", "LARP1"),c("NC1", "LARP6"), c("NC1", "LARP7")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene) + geom_hline(aes(yintercept = med_line), linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + scale_x_discrete(limits = c("none","NC1","SSB", "LARP1","LARP6","LARP7"))
```

# ALL -7 siRNA trsfx data!

```{r, }
m7Dat <- bind_rows(filt28, filt7, R6_spots_filt, R7_spots_filt, .id = "round")

m7Dat %>% group_by(gene,siRNA,image,cell) %>% summarize(numspots = n()) %>% ggplot(aes(x = gene, y = numspots, fill = gene)) + geom_boxplot(outlier.shape = NA) + theme_cowplot() + facet_wrap(.~siRNA) + EnvStats::stat_n_text(y.pos = -25) + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + guides(fill = FALSE)

#try to normalize each imaging round using bottom 25% of cells
m7Dat_norm <- m7Dat %>% filter(gene != "Lox") %>% group_by(round) %>% summarise(minPosZ = quantile(as.numeric(Pos_Z),0.25)) %>% left_join(m2Dat) %>% mutate(Position_In_Z = (as.numeric(Pos_Z) - minPosZ +2000)/1000) 

m7Dat_norm %>% filter(gene!= "Lox") %>% group_by(gene,siRNA,image,cell,round) %>% summarise(meanPosZ = median(Position_In_Z), na.rm = TRUE) %>% mutate(Rimg = paste(image,round,sep = "_")) %>% ggplot(aes(x = Rimg, y = meanPosZ, col = round)) + geom_boxplot() + geom_point(aes(shape = as.character(cell))) + facet_grid(gene~siRNA) + theme_cowplot()

#image 1 for RPS28 is weird.
m7Dat_norm %>% filter(gene != "Lox",gene == "FF") %>% group_by(gene,siRNA,image,cell,round) %>%  summarise(medPosZ = median(Position_In_Z,na.rm = TRUE) ) %>% mutate(Rimg = paste(round,image,sep = "_")) %>% ggplot(aes(x = Rimg, y = medPosZ,col = round)) + geom_boxplot() + geom_point(aes(shape = as.character(cell))) + facet_grid(gene~siRNA) + theme_cowplot() + coord_cartesian(ylim = c(0,6))


#m7Dat_norm2 <- m7Dat_norm %>% filter(!(gene = & siRNA = & round = & image = ))


med_line <- m7Dat_norm %>% filter(gene == "FF", siRNA == "NC1") %>% pull(Position_In_Z) %>% median(na.rm = TRUE)

m7Dat_norm %>% filter(gene != "Lox") %>% filter(siRNA == "NC1") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(yintercept = med_line, linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))


med_line <- m7Dat_norm %>% filter(gene == "FF") %>% group_by(siRNA) %>% summarise(med_line= median(Position_In_Z,na.rm = TRUE))

m7Dat_norm %>% filter(gene != "Lox") %>% left_join(.,med_line, by = "siRNA") %>% ggplot(aes(x = gene, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("FF", "RPL7"), c("FF", "RPL7mut"),c("RPL7", "RPL7mut"), c("FF", "RPS28"), c("FF", "RPS28mut"),c("RPS28", "RPS28mut")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~siRNA) + geom_hline(aes(yintercept = med_line), linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5))

med_line <- m7Dat_norm %>% filter(siRNA == "NC1") %>% group_by(gene) %>% summarise(med_line= median(Position_In_Z,na.rm = TRUE))

m7Dat_norm %>% filter(gene != "Lox") %>% left_join(.,med_line, by = "gene") %>% ggplot(aes(x = siRNA, y = Position_In_Z)) + geom_violin(aes(fill = gene, alpha = gene))+ geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.2) + theme_cowplot() + stat_compare_means(comparisons = list(c("NC1", "none"), c("NC1", "SSB"), c("NC1", "LARP1"),c("NC1", "LARP6"), c("NC1", "LARP7")), method = "wilcox.test") + labs(x = "", y = "Position in Z") + guides(fill = FALSE, alpha = FALSE) + facet_wrap(.~gene) + geom_hline(aes(yintercept = med_line), linetype = "dashed") + scale_fill_manual(values = c("#808080","#e8c040", "#e8c040", "#b82080", "#b82080")) + scale_alpha_manual(values = c(1,1,0.5,1,0.5)) + scale_x_discrete(limits = c("none","NC1","SSB", "LARP1","LARP6","LARP7"))

```

