---
title: "FISH analysis for Neurons"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr)
library(cowplot)
```

## This code is useful for analyzing neurite vs soma spot data from FISH-quant
### This example starts with the summary Mature save file from Batch mode

```{r,read in FISH-quant summary dat}

#for some reason I have two different summary files

CAD28_summary <- as_tibble(read.csv("__FQ_batch_summary2_MATURE_201102.txt", skip = 4, header = TRUE, sep = "\t"))
CAD28_more_summary <- as_tibble(read.csv("__FQ_batch_summary2_MATURE_201104.txt", skip = 4, header = TRUE, sep = "\t"))


CAD28 <- rbind(CAD28_summary, CAD28_more_summary) %>% # this combines the two data files
  separate(FILE, sep = "_", into = c("gene", "image", "extra", "STACK", "extra2", "outline")) %>% # this organizes the columns and may be different depending on your image names
  mutate(cell = as.numeric(substr(CELL, 6, 6)), # cleans the cell number
         cell = ifelse(cell %% 2 == 0, "neurite", "soma")) %>% # assigns even cells as neurites and odd cells as somas
  dplyr::select(gene, image, cell, AREA_cell, N_total, N_thres_Total) # keep the good stuff

```

## Sometimes we are interested in more than just the aboslute number of spots in the neurite vs the soma
### here we calculate spots in neurite relative to the spots in their soma. This is a ratio but can be thought of as a percent localized since the soma contributes many more spots than the neuite

```{r, compare neurites to their somas}
#this creates neurite/soma values for total spots
n_s_tot <- CAD28 %>% 
  select(gene, image, cell, N_total) %>% 
  group_by(image) %>% # group by cells in image
  mutate(id=rep(1:(n()/2),each = 2)) %>% # add a unique ID to keep R happy
  spread(key = cell, value = N_total) %>% # for each cell spread the total spots between neurite and soma
  mutate(n_s_tot = neurite/soma) %>% # calculate total spots neurite/soma
  select(gene, image, n_s_tot) %>% # keep the good stuff
  ungroup() %>% 
  mutate(id = c(1:nrow(.)))

# this creates neurite/soma values for thesholded spots (same as above)
n_s_thresh <- CAD28 %>% 
  select(gene, image, cell, N_thres_Total) %>% 
  group_by(image) %>% 
  mutate(id=rep(1:(n()/2),each=2)) %>% 
  spread(key = cell, value = N_thres_Total) %>%
  mutate(n_s_thresh = neurite/soma) %>% 
  select(gene, image, n_s_thresh) %>% 
  ungroup() %>% 
  mutate(id = c(1:nrow(.)))

# join these data sets and merge back with un-normalized data

rel_dat28 <- left_join(n_s_tot, n_s_thresh)
```

## Now for some sweet plots

```{r,  QC plots for sanity}
# its good to check that your somas have more spots than neurites
CAD28 %>% ggplot(aes(x = gene, y = N_thres_Total, fill = cell)) + 
  geom_boxplot(width = 0.25) + 
  geom_point(alpha = 0.1, position = position_jitterdodge()) + 
  theme_cowplot()  + 
  labs(x = "", y = "Total Number of Thresholded Spots")

# its also useful to see that your neurites/somas are simlar sizes across conditions
CAD28 %>% ggplot(aes(x = gene, y = AREA_cell, fill = cell)) + 
  geom_boxplot(width = 0.25) + 
  geom_point(alpha = 0.1, position = position_jitterdodge()) + 
  theme_cowplot() + 
  labs(x = "", y = "Cell Area (pixels)")

```

## These plots are probably more interesting

```{r, Final plots for localization}
my_comparisons = list(c("005", "28"), c("005", "28mut"), c("28","28mut")) # this is for stat_compare_means()

# looking at absolute spots in the neurites
CAD28 %>% 
  filter(cell == "neurite") %>% # only want the neurites
  ggplot(aes(x = gene, y = N_thres_Total, fill = gene, alpha = gene)) + 
  geom_point(alpha = 0.1, position = "jitter") + 
  geom_violin() + 
  geom_boxplot(width = 0.25) + 
  stat_compare_means(comparisons = my_comparisons, method = "wilcox.test") + 
  theme_cowplot() + 
  guides(fill = FALSE, alpha = FALSE) + 
  labs(x = "", y = "Thresholded Spots in Neurite") + 
  EnvStats::stat_n_text() + 
  scale_x_discrete(limits = c("005", "28", "28mut"), 
                   labels = c("FF", "RPS28", "RPS28mut")) + 
  scale_fill_manual(values = c("#808080", "#b82080", "#b82080")) + 
  scale_alpha_manual(values = c(1,1,0.25))


# this normalizes neurite spots to soma spots
rel_dat28 %>% 
  ggplot(aes(x = gene, y = n_s_thresh, fill = gene, alpha = gene)) + 
  geom_point(alpha = 0.1, position = "jitter") + 
  geom_violin() + 
  geom_boxplot(width = 0.25) + 
  stat_compare_means(comparisons = my_comparisons, method = "wilcox.test") + 
  theme_cowplot() + 
  guides(fill = FALSE, alpha = FALSE) + 
  labs(x = "", y = "spots in Neurite / Soma") + 
  EnvStats::stat_n_text() + 
  scale_x_discrete(limits = c("005", "28", "28mut"), 
                   labels = c("FF", "RPS28", "RPS28mut")) + 
  scale_fill_manual(values = c("#808080", "#b82080", "#b82080")) + 
  scale_alpha_manual(values = c(1,1,0.25))


```

# Another way to analyze Fish-quant data is to use ALL the spots!
## This code is useful for analyzing neurite vs soma spot data from FISH-quant
### This example starts with the All spots save file from Batch mode

```{r, read in all spot data}
all_spot_cad <- as_tibble(read.csv("21.04.06_CAD_3TOP_FISH/results/_FISH-QUANT__all_spots_210407.txt", header = TRUE, skip = 13, sep = "\t"))

all_spot_cad <- all_spot_cad %>% 
  separate(File, into = c("CAD", "gene","image","stack"), sep = "_") %>% # this may change depending on your image names
  mutate(cell = as.numeric(substr(Cell, 6, 6)), # clean up cell numbers
         cell = ifelse(cell %% 2 == 0, "neurite", "soma"), # assign neurite vs soma (even vs odd)
         image = substr(image,1,2)) %>% # clean up image numbers
  select(gene, image, cell, everything(), -stack) # keep the good stuff

```

## now to filter all the spot data together

```{r, filter some spots!}
# a fast look at some different spot parameters in soma v neurite
all_spot_cad %>% 
  select(gene, cell, SigmaX, SigmaZ, BGD, Pos_Z) %>% 
  gather(-gene,-cell,key = "param", value = "value") %>% 
  mutate(value = as.numeric(value)) %>% 
  ggplot(aes(y=value, group = gene, fill = gene)) + 
  geom_density(alpha = 0.5) + 
  facet_wrap(cell~param, scales = "free", nrow =2) + 
  theme_cowplot()

# now the intensity spot parameters
all_spot_cad  %>% 
  select(gene, cell, AMP, INT_raw, INT_filt) %>% 
  gather(-gene,-cell,key = "param", value = "value") %>% 
  mutate(value = as.numeric(value)) %>% 
  ggplot(aes(y=value, group = gene, fill = gene)) + 
  geom_density(alpha = 0.5) +
  facet_wrap(cell~param, scales = "free",nrow = 2) + 
  theme_cowplot() +
  ylim(0,2000)

# a closer look with each parameter This is where you will decide new thresholds
# The same thresholds should be set for neurites and somas
all_spot_cad %>% 
  select(gene,cell,INT_raw) %>% # INT_raw is the parameter to plot
  gather(-gene,-cell,key = "param", value = "value") %>%
  mutate(value = as.numeric(value)) %>% 
  ggplot(aes(y=value, group = gene, fill = gene)) +
  geom_density(alpha = 0.5) + 
  theme_cowplot() +
  ylim(0,1500) + # you may need to reset this depending on your data
  facet_grid(.~cell) + 
  geom_hline(yintercept = 1150) # this is your minimum threshold keep spots that are higher!

all_spot_cad %>% 
  select(gene,cell,BGD) %>% # Background is the parameter to plot
  gather(-gene,-cell,key = "param", value = "value") %>% 
  mutate(value = as.numeric(value)) %>%
  ggplot(aes(y=value, group = gene, fill = gene)) + 
  geom_density(alpha = 0.5) +
  theme_cowplot() + 
  ylim(100,900) + # you may need to reset this depending on your data
  facet_grid(.~cell) +
  geom_hline(yintercept = 700) # this is your maximum threshold keep spots that are lower!

all_spot_cad %>% 
  select(gene,cell,Pos_Z) %>% # position in Z is the parameter to plot
  gather(-gene,-cell,key = "param", value = "value") %>%
  mutate(value = as.numeric(value)) %>%
  ggplot(aes(y=value, group = gene, fill = gene)) +
  geom_density(alpha = 0.5) +
  theme_cowplot()  + 
  facet_grid(.~cell) + 
  geom_hline(yintercept = 1400) + # this is the lower threshold
  geom_hline(yintercept = 9000) # this is the upper threshold

all_spot_cad %>% 
  select(gene,cell,SigmaX) %>% # sphericity in XY is the parameter to plot
  gather(-gene,-cell,key = "param", value = "value") %>% 
  mutate(value = as.numeric(value)) %>%
  ggplot(aes(y=value, group = gene, fill = gene)) + 
  geom_density(alpha = 0.5) +
  theme_cowplot()  + 
  facet_grid(.~cell) + 
  geom_hline(yintercept = 450) # this is the upper threshold

all_spot_cad %>% 
  select(gene,cell,SigmaZ) %>% # sphericity in Z is the parameter to plot
  gather(-gene,-cell,key = "param", value = "value") %>% 
  mutate(value = as.numeric(value)) %>%
  ggplot(aes(y=value, group = gene, fill = gene)) + 
  geom_density(alpha = 0.5) + 
  theme_cowplot() + 
  facet_grid(.~cell) + 
  geom_hline(yintercept = 750) # this is the upper threshold


# Now that you have plotted and decided where thesholds should be, you must filter the original dataset
# I like to keep my filtering as simple as possible, usually I only limit INT_raw
CAD_filt <- all_spot_cad %>% 
  filter(as.numeric(INT_raw) > 1150, 
         as.numeric(SigmaX) < 450, 
         as.numeric(SigmaZ) < 750, 
         as.numeric(Pos_Z) > 1400,
         as.numeric(Pos_Z) < 9000, 
         as.numeric(BGD) < 700)

```

# Now to check if your filtering makes sense

```{r, }
# plotting total spots per cell can be informative
# we expect somewhere between 200-500 spots in each soma
# neurites should have much less spots
CAD_filt %>% 
  group_by(gene,image,cell) %>% 
  summarize(numspots = n()) %>% # sum all spots in a cell (soma or neurite)
  ggplot(aes(x = gene, y = numspots, fill = cell)) + 
  geom_boxplot() + 
  theme_cowplot()

```

# Now to see if your spots are localized

```{r, plots, warning = FALSE}
# The simplest way to tell is to compare number of spots in the neurite
CAD_filt %>% 
  group_by(gene,image,cell) %>%
  summarize(numspots = n()) %>% # sum all spots in a cell (soma or neurite)
  filter(cell == "neurite") %>% # only keep neurite spots
  ggplot(aes(x = gene, y = numspots, fill = gene)) + 
  geom_boxplot(outlier.shape = NA) +
  theme_cowplot() +
  stat_compare_means(comparisons = list(c("pTL005", "mut3TOP"), c("pTL005", "WT3TOP"),c("mut3TOP", "WT3TOP")), method = "wilcox.test") + # These comparisons will likely change
  labs(x = "", y = "Spots in Neurite") + guides(fill = FALSE)

# Usually a better way is to normalize neurite spots to soma spots (this code is messy)
CADfilt_norm <- CAD_filt %>% 
  group_by(gene,image,cell) %>% 
  summarize(N_thres_Total = n()) %>% # sum all spots in a cell (soma or neurite)
  ungroup() %>%
  select(gene, image, cell, N_thres_Total) %>% 
  group_by(gene,image) %>% 
  spread(key = cell, value = N_thres_Total) %>%
  mutate(n_s_thresh = neurite/soma) %>% # calculate neurite spots / soma spots
  select(gene, image, n_s_thresh) %>% 
  ungroup() %>% left_join(., CAD_filt %>% 
                            group_by(gene,image,cell) %>%
                            summarize(N_thres_Total = n()) %>%
                            ungroup() %>%
                            select(gene, image, cell, N_thres_Total)) 

# now plot the normalized data
CADfilt_norm %>% 
  select(-N_thres_Total) %>% 
  unique() %>%
  ggplot(aes(x = gene, y = n_s_thresh))  + 
  geom_violin(aes(fill = gene, alpha = gene)) + 
  geom_boxplot(aes(fill = gene, alpha = gene), outlier.shape = NA, width = 0.1) +
  geom_point(alpha = 0.25, position = "jitter") +
  theme_cowplot() +
  stat_compare_means(comparisons = list(c("pTL005", "mut3TOP"), c("pTL005", "WT3TOP"),c("mut3TOP", "WT3TOP")), method = "wilcox.test") + 
  labs(x = "", y = "Spots in Neurite/Soma") + # add axis labels
  guides(fill = FALSE, alpha = FALSE) + 
  scale_x_discrete(limits = c("pTL005", "WT3TOP", "mut3TOP"), # change the order of x axis
                   labels = c("Firefly", "WT 3'TOP", "mut 3'TOP")) + # change the name on x axis
  scale_fill_manual(values = c("#00a0b0", "#808080", "#00a0b0")) + # pick pretty colors!
  scale_alpha_manual(values = c(0.3,1,1)) # changes the see-through-ness of boxplots

```

